Succinct representations for abstract interpretation

### 2011-11-01 papers/PLDI2012/implicitization.tex
traitement de quelques remarques

\DM{Julien: pour la guided analysis, a priori ça arrive souvent cette histoire d'edge pas prise car non encore prenable?}
\JH{Oui, ca arrive regulierement}
In the event that a node is reachable only by a single control-flow edge (which may occur because of dead code, or during the first phases of guided static analysis), the $\phi$ operation reduces to a copy of the values flowing from that edge. In this case, our tool just propagates symbolic values through the predecessor node, without introducing $\phi$-variables.

@@

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm.
\MM{Si y'a la place, on peut dire un truc du style: ``This can be
  explained by the fact that these algorithms start on a small subset
  of the graph, and then may need fewer iterations on the complete
  graph.''}
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

@@

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields weaker invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator.
\DM{Ici on pourrait citer Monniaux+Le Guen si c'etait publie!}
\MM{Oui, ça fait un peu [citation needed] comme phrase ;-)}
The Octagon domain appears to be much better than intervals; this is
unsurprising since in most programs and libraries, bounds on loop indices are
non constant: they depend on some parameters (array sizes etc.).

>>>>

In the event that a node is reachable only by a single control-flow edge (which may occur because of dead code, or during the first phases of guided static analysis), the $\phi$ operation reduces to a copy of the values flowing from that edge. In this case, our tool just propagates symbolic values through the predecessor node, without introducing $\phi$-variables.

@@

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm.
This seems due to the fact that these algorithms start on a small subset
of the graph, and then may need fewer iterations on the complete graph.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

@@

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields weaker invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator~\cite{Monniaux_LeGuen2011}.
The Octagon domain appears to be much better than intervals; this is
unsurprising since in most programs and libraries, bounds on loop indices are
non constant: they depend on some parameters (array sizes etc.).
